\mytitle

### 2016-09-16 pdocs/thesis/article-section-2.tex
working on Aki's comments on article

\begin{figure}[htb!]
\centering
\begin{tikzpicture}
\coordinate (S) at (2.5,5);
\draw (0,5) -- (4,5) ;
\draw (0,0) -- (4,0) ;
\draw (2,0) -- (2,5) ;
\draw (1.5,0) -- (S); 
\node[above] at (S) [align=center] {\large{$\sigma<f_y$}};
\end{tikzpicture}
\hspace{1cm}
\begin{tikzpicture}
\coordinate (S) at (3,5);
\draw (0,5) -- (4,5) ;
\draw (0,0) -- (4,0) ;
\draw (2,0) -- (2,5) ;
\draw (1,0) -- (1,2.5) -- (3,2.5) -- (S); 
\node[above] at (S) [align=center] {\large{$\sigma=f_y$}};
\end{tikzpicture}
\caption{Axial stress distribution for bending under elastic and plastic loads.}
\label{fig:wp}
\end{figure}

>>>>

\begin{figure}[htb!]
\centering
\begin{tikzpicture}
\coordinate (S) at (2.5,5);
\draw (0,5) -- (4,5) ;
\draw (0,0) -- (4,0) ;
\draw (2,0) -- (2,5) ;
\draw (1.5,0) -- (S); 
\node[above] at (S) [align=center] {\large{$\sigma<f_y$}};
\node[anchor=west] at (-2,3) {
\begin{tabular}{l}
Under elastic load\\
stress increases\\
linearly from zero\\
at neutral axis to\\
maximum value at \\
surface of body
\end{tabular}
};
\end{tikzpicture}
\hspace{1cm}
\begin{tikzpicture}
\coordinate (S) at (3,5);
\draw (0,5) -- (4,5) ;
\draw (0,0) -- (4,0) ;
\draw (2,0) -- (2,5) ;
\draw (1,0) -- (1,2.5) -- (3,2.5) -- (S); 
\node[above] at (S) [align=center] {\large{$\sigma=f_y$}};
\node[anchor=west] at (3,3) {
\begin{tabular}{l}
Under plastic load\\
stress is at yield\\
level over full\\
cross section
\end{tabular}
};
\end{tikzpicture}
\caption{Axial stress distribution over cross section for bending under elastic and plastic loads.}
\label{fig:wp}
\end{figure}
